### 2023-04-03 paper/content.tex

\begin{enumerate}
\item Calculate the \textit{total gradient amplitude} (TGA), also known as the 3D analytic signal \citep{Roest1992Magnetic}, of the observed vertical   component of the magnetic field. The TGA is entirely positive and tends to be more concentrated on top of the magnetic field sources than the observed magnetic field. The derivative calculation also acts as a high-pass filter, removing long-wavelength noise from the data.
\item Apply a contrast stretching method to re-scale the TGA to a new range   defined by the lower and upper percentiles of the data in order to highlight the weaker signals, either coming from small or from deep-seated particles.
%\item To enhance the quality of an image before the blob detection, we can also apply a common two-step approach that involves using a median filter and an unsharp mask filter \citep{VanderWalt2014}. The median filter reduces high-frequency noise (e.g., salt and pepper noise) in the image at the cost of smoothing slightly the edges, and the unsharp mask filter enhances the contrast and sharpness of edges. By applying a median filter followed by an unsharp mask filter, we can significantly improve the visual quality of an image while preserving the edges and the details.  
\item Use the Laplacian of Gaussian (LoG) method \citep{VanderWalt2014} on the   re-scaled TGA data to estimate the position and size of data windows containing the signal of each particle.
\end{enumerate}

@@

\begin{equation}
\label{CgjOtKLQKT}
\begin{bmatrix}
\dfrac{\mu_0}{4\pi}\dfrac{3(z_1 - z_c)(x_1 - x_c)}{r_1^5}
& \dfrac{\mu_0}{4\pi}\dfrac{3(z_1 - z_c)(y_1 - y_c)}{r_1^5}
& \dfrac{\mu_0}{4\pi}\left(\dfrac{3(z_1 - z_c)^2}{r_1^5} - \dfrac{1}{r_1^3}\right)
\\
\dfrac{\mu_0}{4\pi}\dfrac{3(z_2 - z_c)(x_2 - x_c)}{r_2^5}
& \dfrac{\mu_0}{4\pi}\dfrac{3(z_2 - z_c)(y_2 - y_c)}{r_2^5}
& \dfrac{\mu_0}{4\pi}\left(\dfrac{3(z_2 - z_c)^2}{r_2^5} - \dfrac{1}{r_2^3}\right)
\\
\vdots & \vdots & \vdots
\\
\dfrac{\mu_0}{4\pi}\dfrac{3(z_N - z_c)(x_N - x_c)}{r_N^5}
& \dfrac{\mu_0}{4\pi}\dfrac{3(z_N - z_c)(y_N - y_c)}{r_N^5}
& \dfrac{\mu_0}{4\pi}\left(\dfrac{3(z_N - z_c)^2}{r_N^5} - \dfrac{1}{r_N^3}\right)
\end{bmatrix}
\begin{bmatrix}
m_x \\ m_y \\ m_z
\end{bmatrix}
=
\begin{bmatrix}
{b_z}_1 \\ {b_z}_2 \\ \vdots \\ {b_z}_L
\end{bmatrix}
\ ,
\end{equation}

@@

\noindent
The estimated dipole moment vector $\hat{\mathbf{m}}$ can be converted into declination $D$, inclination $I$, and magnitude $m$, which are more intuitive quantities for interpreting paleomagnetic results, like so

\begin{equation}
  \label{eq_vector_to_incdec}
\begin{aligned}
I &= \tan^{-1}\left(\dfrac{m_z}{\sqrt{m_x^2 + m_y^2}}\right) \ , \\
D &= \tan^{-1}\left(\dfrac{m_x}{m_y}\right) \ , \\
m &= \sqrt{m_x^2 + m_y^2 + m_z^2} \ .
\end{aligned}
\end{equation}

It is important to note that these are not paleomagnetic declination and inclination angles, but are instead related to the sample coordinate system. To obtain the paleomagnetic direction, the dipole moment vector must be rotated to the sample field orientation prior to the application of Equation~\ref{eq_vector_to_incdec}.

In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors, equipment inaccuracies, and sensor limitations. This noise added to the observed data vector affects the solution of the estimated parameter vector $\mathbf{m}$, regardless of the method used. Assuming that the noise in the observed data measure is independent and of variance ${\sigma_0}^2$, the latter given by (i) the squared standard deviation used in synthetic cases (e.g., pseudo-random normal distributions) or (ii) the sensor limitations for real samples. Nevertheless, if the sample's variance is not known, one can typically estimate it by using the \emph{$\chi^2$} statistic, \citep[Eq.~\ref{chi_square},][]{Aster2019}, which depends on the residual sum of squares and the degrees of freedom (\emph{v}), the latter being the difference between the number of observed data points (N) and the parameters (m).

\begin{equation}
  \label{chi_square}
\begin{aligned}
\large \sigma_0^2 = {\chi}^2 = \frac{\sum{\left( b_z - {b_{z}}_{dipole} \right)}^2}{N-m}
\end{aligned}
\end{equation}

\begin{equation}
\label{lPOQaqlV3N}
\mathbf{C} =
\begin{bmatrix}
\sigma_x^2 & \sigma_{xy} & \sigma_{xz} \\
\sigma_{yx} & \sigma_y^2 & \sigma_{yz} \\
\sigma_{zx} & \sigma_{zy} & \sigma_z^2
\end{bmatrix}
=
\sigma_0^2 (\mathbf{A}^T\mathbf{A})^{-1}
\end{equation}

From the main diagonal of $\mathbf{C}$ we can obtain the variances of the
declination $\sigma_D^2$, inclination $\sigma_I^2$, and magnitude $\sigma_m^2$
by the propagation of uncertainties

\begin{equation}
\label{uncertanties}
\begin{aligned}
\sigma_D^2 &= \dfrac{m_y^2\sigma_x^2 + m_x^2\sigma_y^2}{\left(m_x^2 + m_y^2\right)^2} \ , \\
\sigma_I^2 &= \dfrac{m_x^2 m_z^2 \sigma_x^2 + m_y^2 m_z^2 \sigma_y^2 + \left(m_x^2 + m_y^2\right)^2\sigma_z^2}{\left(m_x^2 + m_y^2\right) m^4} \ , \\
\sigma_m^2 &= \dfrac{m_x^2\sigma_x^2 + m_y^2\sigma_y^2 + m_z^2\sigma_z^2}{m^2} \ .
\end{aligned}
\end{equation}

@@

It is relevant to highlight that parameters retrieved during inversion procedures do not always explain the observed data, so it is necessary to evaluate the fitting of the predicted data obtained with these parameters. \cite{Fu2020} apply the calculation of the "non-dipolarity parameter (\emph{D})" by calculating the coefficient of determination ($R^2$, Eq.~\ref{R2}). The latter has a maximum value of 1, if \emph{D} is close enough to this value, a simple dipole model is able to explain the measured data. On the other hand, low values of $R^2$ indicate that the predicted model does not explain the observed data. \cite{CortesOrtuno2021} use another approach for the evaluation of the predicted model fit, called signal-to-noise ratio (SNR), here we modified it to be given in decibels (Eq.~\ref{SNR}). SNR is the trade-off between the signal and its associated noise acquired during the measurement by any sensor. The higher the SNR values the better it will be the fit of the predicted model. For a signal to be “visible”, \cite{Strum2014} suggest an SNR value of at least 3, which means the signal is 3 times bigger than the noise. Thus, both $R^2$ and the concept of SNR are appropriate to be used as criteria filtering for reliability for dipolar inversions.

\begin{equation}
\label{R2}
\begin{aligned}
\large R^2 = 1 - \frac{ \sum{\left( b_z - {b_{z}}_{dipole} \right)}^2 }{\sum{\left( b_z - \bar{b_z} \right)}^2}
\end{aligned}
\end{equation}

\begin{equation}
\label{SNR}
\begin{aligned}
\large SNR = 10 \log_{10}{\left( \frac{{{\sigma}^2}_{dipole}}{{{\sigma}^2}_{residual}} \right)}
\end{aligned}
\end{equation}

@@

The first synthetic model was performed by generating the vertical magnetic field derived from a simple set of four spheres with similar magnetization intensity and radius, but completely different magnetization directions, contaminated by high-frequency noise. This simplified test model is basically done to investigate the efficiency of the inversions used for Euler positioning and magnetization parameters, thus being a validation of the methodology.

The second model contains one hundred spheres with different magnetization intensities magnetized in two stable directions and similar standard deviation. The magnetic field generated from these sources is corrupted by both low and high-frequency noise. The complexity of this synthetic data seeks to more faithfully emulate real magnetic microscopy data.

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/simple-synthetic-data.png}
  \caption{
    Synthetic data and the various processing steps performed prior to the
    dipole moment inversion. 
    a) The synthetic noise-corrupted $b_z$ observations at 
    $z = \qty{5}{\micro\meter}$ due to four dipolar sources with different
    depths and dipole moment vectors 
    (see Table~\ref{tab_synthetic_simple_results}).
    b) The upward-continued data to $z = \qty{10}{\micro\meter}$ showing
    attenuated short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the 
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source. 
    d) The contrast-stretched TGA, highlighting the signal of all four
    sources, including the weak central source.
    e) The detected source bounding boxes (black squares) that correctly
    identify the signal of all four sources.
    f) The estimated source locations (colored circles) from Euler 
    Deconvolution of the upward-continued data inside each bounding box. 
    The color represents the difference between the true and estimated 
    $z$ coordinates.
  }
  \label{fig_synthetic_simple_data}
\end{figure}

The Figure~\ref{fig_synthetic_simple_data}a shows the vertical component of the magnetic field $b_z$ over a synthetic rock section containing four uniformly magnetized spherical sources. The map covers a surface of $\qty{1000}{\um} \times \qty{1000}{\um}$ with data points in a regular grid of approximate \qty{1}{\um} ($N = 10^6$ observations) obtained at a sensor-sample distance of \qty{5}{\um}. The magnetic field data is contaminated with a pseudo-random noise of normal Gaussian distribution with a zero mean and \qty{20}{\nano\tesla} standard deviation.

We first applied an upward continuation filter (Fig.~\ref{fig_synthetic_simple_data}b) to smooth out high-frequency noise \citep{Blakely1996}, since it strongly affects the first derivatives of the potential field required by the Euler equation. Then, we calculated the magnetic total gradient anomaly map (Fig.~\ref{fig_synthetic_simple_data}c), which is subjected to a stretch contrast filter to highlight as much as possible the weaker intensity sources (Fig.~\ref{fig_synthetic_simple_data}d), 
in order to facilitate the next step. Subsequently, we applied the blob detection algorithm to the contrasted total gradient map to obtain the position of the data window for each source (Fig.~\ref{fig_synthetic_simple_data}e). The ED was performed for each selected source by assuming the structural index of a sphere/punctual source, therefore obtaining the Cartesian coordinates (Fig.~\ref{fig_synthetic_simple_data}f) of each source causing the magnetic potential anomaly in the observed data set (Table~\ref{tab_synthetic_simple_results}).

@@

The central positions of each source obtained with ED were used as an input parameter for inverting the vertical magnetic field. The inversion produced a least squares approximation solution for the vector of Cartesian magnetic moments $m_x, m_y, m_z$ and the corresponding magnetization directions (D and I) and intensity of magnetic moment $m$ (Fig.~\ref{fig_synthetic_simple_results}). We also obtained the uncertainty propagation of this inversion, using equations~\ref{chi_square}-\ref{uncertanties}, as shown in Table~\ref{tab_synthetic_simple_results}.

\begin{table}[t]
  \begin{center}
    \small
    \input{simple-synthetic-results.tex}
  \end{center}
  \caption{Each source positioning and magnetization parameters modeled and recovered by the least square estimator, respectively.}
  \label{tab_synthetic_simple_results}
\end{table}

@@

This test represents a more complex scenario by simulating 100 sources randomly distributed in the imaged area of a synthetic thin section of 2000 x 2000 $\mu m$. The synthetic $b_z$ data were generated on a regular grid with 2 $\mu m$ spacing and 5 $\mu m$ sample-sensor distance. For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensity. The depths vary between 1 and 20 $\mu m$, while the magnetic moment intensity ranges from $10^{-12}$ to $10^{-14}$ $Am^2$.

To add more complexity, we simulate two stable magnetization  directions, both sampled from a pseudo-random Gaussian distribution, this randomness simulates the NRM found in real ferromagnetic particles that vary individually but average out to the inducing field direction. The first group of sources ($n = 70$) has a magnetization mean direction of D = 0°, I = 0°, and a standard deviation of 10°. While the second one ($n = 30$) has a magnetization mean direction of D = 180°, I = 0°, also with standard deviation of 10°. Finally, we contaminated the data with high-frequency normally-distributed pseudo-random noise with zero mean and 50 nT standard deviation, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain. The noise-corrupted synthetic $b_z$ image is shown in Figure~\ref{complex-synthetic-data}a.

\begin{figure}[t]
  \centering
  \includegraphics[width=1\linewidth]{figures/complex-synthetic-data.png}
  \caption{
    a) The synthetic high and low-frequency noise-corrupted $b_z$ observations at 
    $z = \qty{5}{\micro\meter}$ due to two clusters of stable directions simulated. 
    b) Residual anomaly map after the $5^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise, respectively.
    c) The total gradient amplitude (TGA) calculated from the 
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source. 
    d) The contrast-stretched TGA, highlighting the signal of all sources, especially the weaker ones.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the signal of the sources.
    f) The estimated source locations (colored circles) from Euler 
    Deconvolution of the upward-continued data inside each bounding box. 
    The color represents the difference between the true and estimated 
    $z$ coordinates.
  }
  \label{complex-synthetic-data}
\end{figure}

Since now the data have both high and low-frequency noise, we performed a $5^{th}$ degree polynomial fitting to remove the low-frequency wavelength from the signal. Subsequently, we applied an upward continuation to get rid of the high-frequency ones (Fig.~\ref{complex-synthetic-data}b). Followed by the TGA map calculation (Fig.~\ref{complex-synthetic-data}c), stretched-contrast filter (Fig.~\ref{complex-synthetic-data}d), and blob detection algorithm (Fig.~\ref{complex-synthetic-data}e). The positioning result of each source by window detection method is shown in Figure~\ref{complex-synthetic-data}e, where 98 particles out of the original 100 were detected.

The spatiality of the inversion results is one of the key advantages of magnetic microscopy over the classic techniques of paleomagnetism. Therefore, we present the inversion results spatially so that we can evaluate any patterns in their distribution. The depth and dipolar moment of each particle are represented by horizontal and vertical error bars (Fig.~\ref{complex-synthetic-comparison}), respectively. These two variables are useful proxies for reliably determining the range for the width and amplitude range of the vertical component magnetic signal the technique is able to identify, which is crucial to know when evaluating these types of inversion results.

Figure~\ref{complex-synthetic-comparison} shows the difference between the estimated dipole moments and the true values for each of the 98 particles that were identified and the model fitting tests. Firstly, we evaluate the magnetic direction misfits by calculating the module of the angular difference between the true and the estimated magnetization vectors (Fig.~\ref{complex-synthetic-comparison}a). Afterward, we calculate the dipole moment misfits in percentage (~$|~100 \left( m_{true} - m_{estimate}\right)~/~\left(m_{true}\right)~|$~), as shown in Figure~\ref{complex-synthetic-comparison}b). Then, the fitting tests were performed using the equations~\ref{R2}-~\ref{SNR} in an attempt to select which criterion best separates data with good fitting and low errors of direction and dipole moment. Figure~\ref{complex-synthetic-comparison}c shows the R² coefficient, or the \emph{D} parameter of the non-dipolarity test \citep{Fu2020}, representing how well the dipolar model is able to explain the observed data in the given window. On the other hand, the SNR is capable to express the power of the predicted model over its residual, therefore can select which sources are more "visible" by the sensor (Fig.~\ref{complex-synthetic-comparison}d). Consequently yielding results directly proportional to the R² coefficient.

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.75\linewidth]{figures/complex-synthetic-comparison.png}
\caption{
The validation of the result obtained with the inversion was calculated for each individual particle based on the error between the real parameters modeled and their respective recovered values, being (a) the direction and (b) intensity of the magnetic moment, in addition to the $R^2$ score (c) obtained by comparing the forward model and the actual data. The depth and radius of the magnetic sources are also important factors that influence the final result, therefore, these data are given in the form of cross plots, with the vertical bar represented by the depth (1 - 20 $\mu m$) and the horizontal bar by the dipole moment amplitude ($10^{-12}$ to $10^{-14}$ $Am^2$).
}
\label{complex-synthetic-comparison}
\end{figure}

Figure~\ref{complex-synthetic-stereograms} shows stereograms with the directions generated by the modeled (Fig.~\ref{complex-synthetic-stereograms}a) and the estimated vectors (Fig.~\ref{complex-synthetic-stereograms}b) for each source. The distribution of the estimated directions is coincident with the true directions aside from a few sources, the same ones with the higher values of direction misfit (Fig.~\ref{complex-synthetic-comparison}a) which is probably associated with the mutual interference of sources close to each other or within the same window. When filtered to include only data with R\textsuperscript{2} \textgreater 0.95 and SNR \textgreater 10 the obtained direction distribution is closer to the true distribution (Fig.~\ref{complex-synthetic-stereograms}c).

>>>>

\begin{enumerate}
\item Calculate the \textit{total gradient amplitude} (TGA), also known as the 3D analytic signal \citep{Roest1992Magnetic}, of the observed vertical   component of the magnetic field. The TGA is entirely positive and tends to be more concentrated on top of the magnetic field sources than the observed magnetic field. The derivative calculation also acts as a high-pass filter, removing long-wavelength noise from the data.
\item Apply a contrast stretching method to re-scale the TGA to a new range   defined by the lower and upper percentiles of the data in order to highlight the weaker signals, either coming from small or from deep-seated particles.
\item Use the Laplacian of Gaussian (LoG) method \citep{VanderWalt2014} on the   re-scaled TGA data to estimate the position and size of data windows containing the signal of each particle.
\end{enumerate}

@@

\begin{equation}
\label{CgjOtKLQKT}
\begin{bmatrix}
\dfrac{\mu_0}{4\pi}\dfrac{3(z_1 - z_c)(x_1 - x_c)}{r_1^5}
& \dfrac{\mu_0}{4\pi}\dfrac{3(z_1 - z_c)(y_1 - y_c)}{r_1^5}
& \dfrac{\mu_0}{4\pi}\left(\dfrac{3(z_1 - z_c)^2}{r_1^5} - \dfrac{1}{r_1^3}\right)
\\
\dfrac{\mu_0}{4\pi}\dfrac{3(z_2 - z_c)(x_2 - x_c)}{r_2^5}
& \dfrac{\mu_0}{4\pi}\dfrac{3(z_2 - z_c)(y_2 - y_c)}{r_2^5}
& \dfrac{\mu_0}{4\pi}\left(\dfrac{3(z_2 - z_c)^2}{r_2^5} - \dfrac{1}{r_2^3}\right)
\\
\vdots & \vdots & \vdots
\\
\dfrac{\mu_0}{4\pi}\dfrac{3(z_N - z_c)(x_N - x_c)}{r_N^5}
& \dfrac{\mu_0}{4\pi}\dfrac{3(z_N - z_c)(y_N - y_c)}{r_N^5}
& \dfrac{\mu_0}{4\pi}\left(\dfrac{3(z_N - z_c)^2}{r_N^5} - \dfrac{1}{r_N^3}\right)
\end{bmatrix}
\begin{bmatrix}
m_x \\ m_y \\ m_z
\end{bmatrix}
=
\begin{bmatrix}
{b_z}_1 \\ {b_z}_2 \\ \vdots \\ {b_z}_N
\end{bmatrix}
\ ,
\end{equation}

@@

\noindent
The estimated dipole moment vector $\hat{\mathbf{m}}$ can be converted into declination $D$, inclination $I$, and magnitude $m$, which are more intuitive quantities for interpreting paleomagnetic results, like so \citep{Tauxe2018}

\begin{equation}
\label{eq_vector_to_incdec}
\begin{aligned}
I &= \tan^{-1}\dfrac{m_z}{\sqrt{m_x^2 + m_y^2}} \ , \\
D &= \tan^{-1}\dfrac{m_x}{m_y} \ , \\
m &= \sqrt{m_x^2 + m_y^2 + m_z^2} \ .
\end{aligned}
\end{equation}

\noindent
It is important to note that these are not paleomagnetic declination and inclination angles, but are instead related to the sample coordinate system. To obtain the paleomagnetic direction, the dipole moment vector must be rotated to the sample field orientation prior to the application of Equation~\ref{eq_vector_to_incdec}.

In a micromagnetic survey, or any geophysical survey, measurements are affected by noise caused by experimental errors, equipment inaccuracies, and sensor limitations. This noise will affect the estimated parameter vector $\mathbf{\hat{m}}$, regardless of the method used. Assuming that the noise in the observed data is independent and normally distributed with zero mean and variance ${\sigma_0}^2$, we can estimate the variance of the parameters by propagation of uncertainties. In reality, the data variance  ${\sigma_0}^2$ is rarely known and must be estimated using the $\chi^2$ statistic \citep{Aster2019}

\begin{equation}
\label{eq_chi_square}
\hat{\sigma}_0^2 = {\chi}^2 = \dfrac{\|\mathbf{d}^o - \mathbf{A}\hat{\mathbf{m}}\|^2}{N - 3}\ ,
\end{equation}

\noindent
in which $N - 3$  are the degrees-of-freedom. 
The covariance matrix $\mathbf{C}$ of the estimated parameters is then given by \citep{Aster2019}

\begin{equation}
\label{eq_covariance}
\mathbf{C} 
=
\hat{\sigma}_0^2 (\mathbf{A}^T\mathbf{A})^{-1}
=
\begin{bmatrix}
\sigma_x^2 & \sigma_{xy} & \sigma_{xz} \\
\sigma_{yx} & \sigma_y^2 & \sigma_{yz} \\
\sigma_{zx} & \sigma_{zy} & \sigma_z^2
\end{bmatrix}
\ .
\end{equation}

\noindent 
From the main diagonal of $\mathbf{C}$, we can obtain the variances of the 
estimated declination $\sigma_D^2$, inclination $\sigma_I^2$, and magnitude $\sigma_m^2$
by propagation of uncertainties from Equation~\ref{eq_vector_to_incdec}

\begin{equation}
\label{eq_variances}
\begin{aligned}
\sigma_D^2 &= \dfrac{m_y^2\sigma_x^2 + m_x^2\sigma_y^2}{\left(m_x^2 + m_y^2\right)^2} \ , \\
\sigma_I^2 &= \dfrac{m_x^2 m_z^2 \sigma_x^2 + m_y^2 m_z^2 \sigma_y^2 + \left(m_x^2 + m_y^2\right)^2\sigma_z^2}{\left(m_x^2 + m_y^2\right) m^4} \ , \\
\sigma_m^2 &= \dfrac{m_x^2\sigma_x^2 + m_y^2\sigma_y^2 + m_z^2\sigma_z^2}{m^2} \ .
\end{aligned}
\end{equation}

@@

Parameters retrieved during inversion procedures may not always explain the observed data perfectly.
Hence, it is necessary to evaluate how well the predicted data is able to fit the observed data. 
When evaluating the goodness of fit of inversions of magnetic microscopy data, \citet{Fu2020} apply a ``non-dipolarity parameter'' ($D$). 
We note that $D$ is equivalent to the coefficient of determination

\begin{equation}
\label{eq_r2}
R^2 = 1 - \dfrac{\|\mathbf{d}^o - \mathbf{A}\hat{\mathbf{m}}\|^2}{\|\mathbf{d}^o - \bar{b}_z^o\|^2}\ ,
\end{equation}

\noindent
in which $\bar{b}_z^o$ is the mean of the observed data.
$R^2$ has a maximum value of 1, which indicates a perfect fit of the data. 
Values close to 1 can therefore be interpreted to mean that a simple dipole model is able to explain the observed data. 
On the other hand, low values of $R^2$ indicate that the dipole model is not able to explain the observed data.

\citet{CortesOrtuno2021} use the ``signal-to-noise ratio'' (SNR) to evaluate the goodness of fit. 
Here, we define the SNR in a logarithmic decibel scale to make it independent of the scale of the data

\begin{equation}
\label{eq_snr}
\text{SNR} = 10 \log_{10}\dfrac{\sigma^2_d}{\sigma^2_r}\ ,
\end{equation}

\noindent
in which $\sigma^2_d$ is the variance of the observed data and $\sigma^2_r$ is the variance of the residuals $\mathbf{r} = \mathbf{d}^o - \mathbf{A}\hat{\mathbf{m}}$.
The SNR is the trade-off between the signal and its associated noise, which we approximate by the inversion residuals. 
The higher the SNR values (in decibels), the better the fit to the observed data. 
For a signal to be ``visible'', \citet{Strum2014} suggest that $\text{SNR} \ge 3$, which means the signal is at least three times stronger than the noise.
Here, we'll use both $R^2$ and SNR as criteria for filtering out unreliable estimates from our dipole moment inversions.

@@

The first synthetic model was performed by generating the vertical magnetic field ($b_z$) derived from a simple set of four dipoles with similar dipole moments amplitudes, but different inclinations and declinations, contaminated by high-frequency noise. 
The purpose of this model is to investigate the efficiency of the combination of Euler Deconvolution and the dipole moment inversion, thus being a validation of the methodology.

The second model contains 100 dipoles with different dipole moment magnitudes, having inclinations and declinations around two stable directions. 
The magnetic field generated from these sources is corrupted by both low and high-frequency noise. 
The complexity of this synthetic data seeks to more faithfully emulate real magnetic microscopy data.

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/simple-synthetic-data.png}
  \caption{
    Simple synthetic data and the various processing steps performed prior to the dipole moment inversion. 
    a) The synthetic noise-corrupted $b_z$ observations at 
    $z = \qty{5}{\micro\meter}$ due to four dipolar sources with different
    depths and dipole moment vectors 
    (see Table~\ref{tab_synthetic_simple_results}).
    b) The upward-continued data to $z = \qty{10}{\micro\meter}$ showing
    attenuated short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the 
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source. 
    d) The contrast-stretched TGA, highlighting the signal of all four
    sources, including the weak central source.
    e) The detected source bounding boxes (black squares) that correctly
    identify the signal of all four sources.
    f) The estimated source locations (colored circles) from Euler 
    Deconvolution of the upward-continued data inside each bounding box. 
    The color represents the difference between the true and estimated 
    $z$ coordinates.
  }
  \label{fig_synthetic_simple_data}
\end{figure}

Figure~\ref{fig_synthetic_simple_data}a shows the vertical component of the magnetic field $b_z$ over a synthetic rock section containing four dipolar sources.
The map covers a surface of $\qty{1000}{\um} \times \qty{1000}{\um}$, with data points in a regular grid with approximately \qty{1}{\um} spacing ($N = 10^6$ observations) obtained at a sensor-sample distance of \qty{5}{\um}. 
The magnetic field data are contaminated with pseudo-random Gaussian noise with zero mean and \qty{20}{\nano\tesla} standard deviation.

We first applied an upward continuation filter (Figure~\ref{fig_synthetic_simple_data}b) to smooth out the high-frequency noise \citep{Blakely1996}.
This is important because it strongly affects the first derivatives of the field, which are required for the Euler Deconvolution. 
Then, we calculated the total gradient amplitude (Figure~\ref{fig_synthetic_simple_data}c), which was then subjected to contrast stretching to highlight as much as possible the weaker intensity sources (Figure~\ref{fig_synthetic_simple_data}d). 
Subsequently, we applied the blob detection algorithm to the contrast-stretched total gradient amplitude to obtain the position of the data windows for each source (Figure~\ref{fig_synthetic_simple_data}e). 
Euler Deconvolution was then performed for each data window identified by assuming a structural index $\eta = 3$ of a point source, therefore obtaining the Cartesian coordinates (Figure~\ref{fig_synthetic_simple_data}f) of each source. Table~\ref{tab_synthetic_simple_results} shows the true and estimated values of the source coordinates for comparison.

@@

The positions of each source obtained with Euler Deconvolution were used as an input parameter for the dipole moment inversion. 
The estimated inclination ($I$), declination ($D$), and dipole moment amplitude ($m$) are shown in Figure~\ref{fig_synthetic_simple_results} along with the corresponding true values.
Table~\ref{tab_synthetic_simple_results} also shows the true and estimate dipole moments as well as their corresponding standard deviations obtained using Equations~\ref{eq_chi_square}-\ref{eq_variances}.

\begin{table}[tb]
  \begin{center}
    \small
    \input{simple-synthetic-results.tex}
  \end{center}
  \caption{
  True and estimated source positions and dipole moments for the simple synthetic data application.
  Each source positioning and magnetization parameters modeled and recovered by the least square estimator, respectively.}
  \label{tab_synthetic_simple_results}
\end{table}

@@

This test represents a more complex scenario by simulating 100 sources randomly distributed in the imaged area of a synthetic thin section of $\qty{2000}{\um} \times \qty{2000}{\um}$. 
The synthetic $b_z$ data were generated on a regular grid with $\qty{2}{\um}$ spacing and $\qty{5}{\um}$ sensor-sample distance. 
We contaminated the data with high-frequency normally-distributed pseudo-random noise with zero mean and $\qty{50}{\nano\tesla}$ standard deviation, as well as with low-frequency noise in the form of additional deep sources beyond the modeling domain.

For greater fidelity to real samples, the magnetic sources are modeled as dipoles with different depths and magnetic moment intensities. 
The depths vary randomly between 1 and $\qty{20}{\um}$, while the dipole moment intensities range randomly from $10^{-12}$ to $\qty{e-14}{\ampere\m\squared}$. 
The NRM found in real ferromagnetic particles varies individually but averages out to the inducing field direction.
To simulate this behaviour in our synthetic data, we sample the source dipole moment directions from two pseudo-random Gaussian distributions. 
The first group of sources ($M = 70$) are sampled from a distribution  with mean of $D = \ang{0}$ and $I = \ang{0}$ and standard deviation of $\ang{10}$. 
The second group of sources ($M = 30$) are sampled from a distribution with mean of $D = \ang{180}$ and $I = \ang{0}$, also with standard deviation of $\ang{10}$. 
The noise-corrupted synthetic $b_z$ data are shown in Figure~\ref{complex-synthetic-data}a.

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/complex-synthetic-data.png}
  \caption{
    Complex synthetic data and the various processing steps performed prior to the dipole moment inversion.
    a) The synthetic high and low-frequency noise-corrupted $b_z$ observations at 
    $z = \qty{5}{\micro\meter}$ due to two clusters of stable directions simulated. 
    b) Residual anomaly map after the $5^{th}$ degree polynomial signal subtraction and upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise, respectively.
    c) The total gradient amplitude (TGA) calculated from the 
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source. 
    d) The contrast-stretched TGA, highlighting the signal of all sources, especially the weaker ones.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the signal of the sources.
    f) The estimated source locations (colored circles) from Euler 
    Deconvolution of the upward-continued data inside each bounding box. 
    The color represents the difference between the true and estimated 
    $z$ coordinates.
  }
  \label{complex-synthetic-data}
\end{figure}

Since now the data have both high and low-frequency noise, we first fit a $5^{th}$ degree polynomial to the data to remove the low-frequency noise. 
We then followed the same processing steps as for the simple synthetic: upward continuation (Figure~\ref{complex-synthetic-data}b),
TGA calculation (Figure~\ref{complex-synthetic-data}c), contrast stretching (Figure~\ref{complex-synthetic-data}d), blob detection (Figure~\ref{complex-synthetic-data}e), and Euler Deconvolution (Figure~\ref{complex-synthetic-data}e).
A total of 98 sources out of the original 100 were successfully detected by our workflow.

\begin{figure}[tb!]
\centering
\includegraphics[width=0.75\linewidth]{figures/complex-synthetic-comparison.png}
\caption{
The validation of the result obtained with the inversion was calculated for each individual particle based on the error between the real parameters modeled and their respective recovered values, being (a) the direction and (b) intensity of the magnetic moment, in addition to the $R^2$ score (c) obtained by comparing the forward model and the actual data. The depth and radius of the magnetic sources are also important factors that influence the final result, therefore, these data are given in the form of cross plots, with the vertical bar represented by the depth (1 - 20 $\mu m$) and the horizontal bar by the dipole moment amplitude ($10^{-12}$ to $10^{-14}$ $Am^2$).
}
\label{complex-synthetic-comparison}
\end{figure}

The spatiality of the inversion results is one of the key advantages of magnetic microscopy over the classic techniques of paleomagnetism.
Therefore, we present the inversion results spatially so that we can evaluate any patterns in their distribution. 
Figure~\ref{complex-synthetic-comparison} shows the spatial locations of the 98 sources that were identified and the differences between the estimated dipole moments and the true values.
The depth and dipole moment amplitude of each source are represented by horizontal and vertical bars, respectively. 
These two variables are useful proxies for the strength and spatial extent of the signal of each source,
which can tell us about the limitations in strengths and sizes of the source signal that the technique is able to correctly invert.
Figure~\ref{complex-synthetic-comparison}a shows the absolute value of the angular difference between the true and the estimated dipole moment vectors. 
Figure~\ref{complex-synthetic-comparison}b shows the percentage difference between the true and estimated dipole moment magnitudes ($|100 \left( m_{true} - m_{estimated}\right) ~/~ m_{true}|$). 
Figure~\ref{complex-synthetic-comparison}c shows the $R^2$ coefficient (Equation~\ref{eq_r2}), which is equivalent to the non-dipolarity parameter of \citet{Fu2020} and represents how well the dipolar model is able to explain the observed data of each source. 
Figure~\ref{complex-synthetic-comparison}d shows the SNR (Equation~\ref{eq_snr}), which expresses the power of the observed data over that of the inversion residuals.
High SNR values correspond to small inversion residuals which indicate that a dipolar model was able to explain the observed data.
Consequently, the variation of SNR values is similar to that of the $R^2$ coefficient.
Figure~\ref{complex-synthetic-comparison} shows that large errors in the estimated dipole moment direction are associated with low values of $R^2$ and SNR.
Conversely, the correlation between errors in dipole moment magnititude and $R^2$ and SNR is less pronounced, with some poor magnitude estimates being associated with $R^2$ and SNR indicating a good fit of the dipolar model.
It is also noticeable that the majority of cases where the dipole moment direction error is large are associated with deep and low-amplitude sources that are close to shallower or higher-amplitude sources.
These results indicated that $R^2$ and SNR can be used as selection criteria to discard sources with likely high errors in the estimated dipole moment.

\begin{figure}[tb!]
\centering
\includegraphics[width=1\linewidth]{figures/complex-synthetic-stereograms.png}
\caption{
a) Simulation of a thin section of rock with two sets of stable particles uniformly magnetized (dipolar sources) in the average direction of the induced field (0{\textbackslash}textdegree/0{\textbackslash}textdegree and 180{\textbackslash}textdegree/0{\textbackslash}textdegree. b) The estimated vector directions without filtering. c) Filtering criteria to select the sources' magnetic directions with the best fitting determined by the coefficient of determination ($R^ 2 \geq 0.85$) and signal-to-noise ratio (SNR $ \geq 5$).
}
\label{complex-synthetic-stereograms}
\end{figure}
